---
title: "IPL Cricket Shiny Dashboard "
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: cerulean #theme
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(highcharter)
library(viridisLite)
library(forecast)
library(treemap)
library(maps)
library(ggmap)
library(googleVis)
library(DT)
library(plotly)


IPL_MatchesData=read.csv("D:/datavis/ipl/matches.csv",header = TRUE)
IPL_MatchesData<-IPL_MatchesData%>%mutate(Year= format(as.Date(IPL_MatchesData$date,'%m-%d-%Y'),'%Y'))
IPL_DelivData=read.csv("D:/datavis/ipl/deliveries.csv",header = TRUE)
IPL_DelivData<-IPL_DelivData%>%mutate(Year= format(as.Date(IPL_DelivData$date,'%d-%m-%y'),'%Y'))
```

Summary{data-icon="glyphicon-list"}
==================================

ROW 
-----------------------------------------------------------------------

### Total Number of Matches
```{r}
Min_temp_on<-count(IPL_MatchesData)
valueBox(Min_temp_on, icon="fa fa-flag-checkered",color="#1E90FF")
```

### Average Score Rate
```{r}
Max_temp_on<-round(mean(IPL_DelivData$total_runs),2)
valueBox(Max_temp_on, icon="fa-align-center",color="#ffbf00")

```

### Total Runs
```{r}
Mean_temp_on<-sum(IPL_DelivData$total_runs)

valueBox(Mean_temp_on, icon="fa fa-bookmark",color="#9ACD32")
```


Row
----------------------------------

### Matches Data

```{r}
#datatable(IPL_MatchesData, filter="top", selection="multiple", escape=FALSE, 
      #options = list(sDom  = '<"top">lrt<"bottom">ip'))
datatable(head(IPL_MatchesData, 20), options = list(
  columnDefs = list(list(className = 'dt-center', targets = 5)),
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
))
```

Row 
----------------------------------

### Deliveries Data

```{r}
datatable(head(IPL_DelivData, 20), options = list(
  columnDefs = list(list(className = 'dt-center', targets = 5)),
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
))
```

Univariate & Bivariate Plots{data-icon="fa fa-bar-chart"}
==================================

Sidebar {.sidebar}
----------------------------------

```{r}
uiOutput("dropdown_years") #Used to display UIdropdown all columns after uploading
uiOutput("dropdown_numcolumns") #Used to display UIdropdown all columns after uploading
```

Row
----------------------------------

### Bar chart for top 10 players for selected year total runs {.text}

```{r}
plotOutput("freq_yearwise_plot") #Used to plot ggplot based on dplyr table data
```

Row
----------------------------------

### Boxplot for Multiple Numerical columns

```{r}
plotOutput("boxplot")
```


multivariate Plots{data-icon="fa fa-line-chart"}
==================================

Row
----------------------------------

### Linechart for Average runs per ball by over each season and innings

```{r}
plotOutput("runs_ipl")
```

Row
----------------------------------

### Stacked Bar for Total runs scored from 1s to 6s

```{r}
plotOutput("runs_ipl1sto6s")
```

### Scatter Plot for Strike rate for Batsman

```{r}
plotOutput("strratbatsman")
```

Maps{data-icon="glyphicon-map-marker"}
==================================
Row
----------------------------------

### Total Number of Matches played in city wise

```{r}
#Rendering the Total number of matches city wise in GooglevisMap
uiOutput("dynamic")

#render the ui:
output$dynamic <- renderUI({ 
   htmlOutput("myTable")
})

#here is your server activity:
output$myTable <- renderGvis({
IPL_Matchescitylatlong=IPL_MatchesData[!is.na(IPL_MatchesData$city),]%>%group_by(city)%>%summarise(TotalMatches=n())%>%arrange(-TotalMatches)
                        gvisGeoChart(IPL_Matchescitylatlong,"city", colorvar="TotalMatches",
                         
                 options=list(region="IN",displayMode="markers", 
                                       resolution="provinces",
                              width=1024, height=400,colorAxis="{colors:['orange', 'green']}",
                   backgroundColor="lightblue"))
                      
})

```

Motion Chart on IPL Data{data-icon="fa fa-recycle"}
==================================

Row {data-height=550}
----------------------------------

### Motion Chart for Total Number of Wins per Team Year Wise. 
Note: Please open this link in IE Browser to view Motion chart.

```{r}
data<-IPL_MatchesData%>%group_by(season,winner)%>%summarise(Total=n())%>%arrange(season)
data<-na.omit(data)
data<-data[-c(62,25),]
data<-as.data.frame(data)

uiOutput("Motionchartdynamic")

#render the ui:
output$Motionchartdynamic <- renderUI({ 
   htmlOutput("Motionchart")
})
output$Motionchart<-renderGvis(gvisMotionChart(data, idvar="winner", timevar="season",sizevar ="Total",colorvar = "Total"))
```

```{r}
observe({
  teams <- IPL_DelivData %>% select(batting_team)%>%
  distinct()
teams <- rename(teams, team = batting_team)
s_team <- c("KKR","RCB","CSK","KXIP","RR","DD","MI","DC","KTK","PWI","SRH","RPS","GL")
teams <- cbind(teams, s_team)
 nums <- sapply(IPL_MatchesData, is.numeric)    
 numsdelv <- sapply(IPL_DelivData, is.numeric) 
  #rendering the numeric column dropdown at sidebar 
  output$dropdown_numcolumns=renderUI(selectInput(inputId = "select_numcolumn",label = "Select a columns for Boxplot",choices=names(IPL_MatchesData)[nums],multiple = TRUE,selected =names(IPL_MatchesData)[nums][2] ))
  #created a variable for boxplot for selected columns
  output$boxplot=renderPlot(boxplot(IPL_MatchesData[,input$select_numcolumn]))
  #rendering the categorical column dropdown at sidebar
  #output$dropdown_catgcolumns=renderUI(selectInput(inputId = "select_catgcolumn",label = "Select a Categorical columns",choices=names(IPL_MatchesData)[!nums],selected =names(IPL_MatchesData)[nums][1]))
   #rendering the categorical column dropdown at sidebar
   output$dropdown_years=renderUI(selectInput(inputId = "select_Year",label = "Select a Year for Barchart",choices=sort(unique(IPL_DelivData$Year))))
   #Using dplyr and ggplot form a table and plot the bar chart
  output$freq_yearwise_plot=renderPlot(
  ggplot(IPL_DelivData%>%filter(Year==input$select_Year)%>%group_by(batsman)%>%summarise(Total_Runs=sum(total_runs,na.rm=TRUE))%>%arrange(-Total_Runs)%>%head(10),aes(x=batsman,y=Total_Runs))+geom_bar(stat = 'identity',fill = "#0080ff")+geom_text(aes(label=Total_Runs), position=position_dodge(width=0.9), vjust=-0.25))
  
  #Average runs per ball by over each season and innings
  runs_o <- IPL_DelivData%>%
  left_join(IPL_MatchesData, by=c("match_id"="id"))%>%
  group_by(season,inning,over)%>%
  summarize(no=n(),runs =sum(total_runs))%>%
  mutate(avg=runs/no)%>%
  filter(inning!=3,inning!=4)
  output$runs_ipl<-renderPlot(ggplot(runs_o,aes(x=season,y=avg,colour=over,group=over))+
  geom_line(show.legend = TRUE, size =1.25,linetype=1)+
  theme(legend.position="right")+
  theme(legend.direction = "vertical") +
  facet_wrap(~inning)+
  scale_y_continuous(name="average runs per ball")+
  scale_x_discrete(name="season",limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016)))
  
  #"Total runs scored in 1s to 6s"
  runs_cat <- IPL_DelivData %>%
  left_join(IPL_MatchesData,by=c("match_id"="id"))%>%
   left_join(teams,by=c("batting_team"="team"))%>%
  group_by(s_team,batsman_runs)%>%
  summarize(no=n(),runs=sum(total_runs))

runs_cat$batsman_runs <- as.factor(runs_cat$batsman_runs)
 
output$runs_ipl1sto6s<-renderPlot(ggplot(runs_cat,aes(x=s_team,y=runs,label=runs,fill=batsman_runs)) +
  geom_bar(stat = "identity"))
#strike rate for batsman 
Bat_sr<- IPL_DelivData %>%
  left_join(IPL_MatchesData,by=c("match_id"="id"))%>%
   left_join(teams,by=c("batting_team"="team"))%>%
  group_by(batsman)%>%
  summarize(balls=n(),runs=sum(batsman_runs))%>%
  mutate(sr=runs*100/balls)%>%
  arrange(desc(sr))%>%
  mutate(score_group=ifelse(sr<100,"100",ifelse(sr<150,"100-150","150+")))%>%
  mutate(player_lab=ifelse(batsman=="AD Russell","AD Russell",ifelse(batsman=="V Sehwag","V Sehwag",ifelse(batsman=="V Kohli","V Kohli",ifelse(batsman=="CH Gayle","CH Gayle","")))))
 
output$strratbatsman<-renderPlot(ggplot(Bat_sr,aes(x=sr,y=runs,colour=score_group,size=runs))+
  geom_jitter(show.legend = TRUE,alpha=.75)+
      theme(legend.position="right")+
    theme(legend.direction = "vertical") +
    geom_text(aes(label=player_lab,hjust=-.25, colour="red"))+
  scale_y_continuous(name="Runs")+
    scale_x_continuous(name="strike rate"))

})

```

